---
title       : Interactive Regression Analysis Tool
subtitle    : A Shiny Application 
author      : Julie
job         : 
framework   : deckjs      # {io2012, html5slides, shower, dzslides, ...}
deckjs      : {theme: web-2.0}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : mathjax      # {mathjax, quiz, bootstrap, shiny, interactive}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Interactive Regression Analysis Tool
### A Shiny Appliation

`r date()`

---

## Overview
This shiny application provides an interactive tool for data visualizationand regression analysis with control widgets. 

>- Dataset swiss from preloaded R datasets package is used for this tool

>- There are two components of the main panel: User Interface and Data Analysis Output

>- User Inferface component includes two panels 
>> * Model Input
>> * Help

>- Data Analysis Ouptut components includes four panels
>>* Data
>>* Summary Statistics
>>* Scatterplot
>>* Regression

--- 
## User Interface

- Model Input 
>* A checkox widget is provided for users to choose the variables for data analysis 
>* Fertility is preselected as dependent variable for regression analysis
  
- Help
>* describes the background and how to use this shiny app

--- 
## Data Analysis Output I
- Data Panel display data table with widget for users to control the number of rows to show (i.e. 3 rows)

```{r,echo=FALSE}
head(swiss,n=4)
```
- Summary Statistics Panel dislays the summary statistics of the Fertility variables and user selected variables(i.e. Agriculture, Examination and Education selected )

```{r,echo=FALSE}
summary(swiss[,c("Fertility","Agriculture", "Examination","Education")])
```

---
## Data Analysis Output II
- Scatterplot Panel displays the scatterplot of the Fertility variable and user selected variables

- Regression Panel displays coefficient tables of mulitple linear regression model of regressing Fertility on user chosen independent variables (i.e. Agriculture,Examination,Education)
```{r, echo=FALSE}
fit <- lm(Fertility~Agriculture+Examination+Education,data=swiss)
summary(fit)$coef
```
